%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Andrei-Niculae Petre
\documentclass[margin,line]{resume}

\RequirePackage{color}
%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Andrei-Niculae PETRE}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

	address: Str Aleea Terasei Nr. 3, Bl. E3, Sc. 1, Ap. 5, Sector 4, 041771 Bucharest, Romania\\
	mobile: +40 727 029 961              \\
	e-mail:  \href{mailto:p31andrei@gmail.com}{p31andrei@gmail.com}  \vspace{0mm}\\\vspace{-4.5mm}\\%
	links: \href{https://github.com/andreip/}{github}, \href{http://www.linkedin.com/profile/view?id=143805798}{linkedin}

    %__________________________________________________________________________________________________________________
    % Objective
    \section{\mysidestyle Objective}

	Software Engineering Intern 


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Politehnica University of Bucharest}, Romania \hfill \textbf{ October 2010 -- present}\vspace{1mm}\\%
	\small{\textbf{Faculty of Automatic Control and Computer Science}}\\
    \textsl{Computer Science - Undergraduate (Class of 2014)}
%    \begin{list2}
%        \item Expected graduation date: July 2014
%    \end{list2}\vspace{-1mm}


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

	\vspace{1.2mm}\href{http://www.ubervu.com}{\textbf{uberVU}}\vspace{1.5mm}\\
	\vspace{1mm} \textsl{Software Developer} \hfill \textbf{June 2012 -- September 2013}\\
	I have worked in becoming a full stack developer, from coffeescript to providing the API in django, to using our automatic
	deploy system and integrating it elsewhere, to touching some of core components of our data acquisition controllers. Also
	did unit, integration and some acceptance testing with selenium.  We developed our own single page app coffeescript framework
	(open source), \href{https://github.com/uberVU/mozaic}{mozaic}. It relies on backbone.js and publish-subscribe design pattern.\vspace{1.5mm}\\
	\small{Reference to \textbf{Bogdan Sandulescu} (CTO, uberVU) - e-mail: \href{mailto:bogdans83@gmail.com}{bogdans83@gmail.com}}\\
	\small{Reference to \textbf{Andrei Ismail} (Developer, uberVU) - e-mail: \href{mailto:iandrei@gmail.com}{iandrei@gmail.com}}

	\vspace{1.2mm}\textbf{Politehnica University of Bucharest}, Romania \vspace{1.5mm}\\
	\vspace{1mm} \textsl{Teaching Assistant} \hfill \textbf{October 2013 -- February 2014}\\
	Teaching assistant for undergraduate Analysis of Algorithms course.
	My tasks include, but are not limited to: teach during laboratory classes, create materials for laboratory classes,
	evaluate homeworks done by students.\vspace{1.5mm}\\
	\textit{Contains:} pseudocode, complexities, turing machine, calculability, NP-completeness etc.\vspace{1.5mm}\\
	\small{Reference to \textbf{Matei Popovici} (Analysis of Algorithms Professor) - e-mail: \href{mailto:pdmatei@gmail.com}{pdmatei@gmail.com}}

	\vspace{1.2mm}\href{http://aimas.cs.pub.ro/}{\textbf{AI-MAS Laboratory}}\vspace{1.5mm}\\
	\vspace{1mm} \textsl{Student Developer, mentored by Andrei Ismail} \hfill \textbf{June 2011 -- September 2011}\\
	Developed a homework for the faculty's AI class (4th year subject). The homework consists of programming a robot to explore an infinite
	grid with obstacles, looking for resources. Used git and added unit tests for homework. Built a Linux minimal virtual machine (VMWare-based)
	with the unit-testing framework on it, used for integrating the homework with the open-source automated homework evaluation
	utility, \href{https://elf.cs.pub.ro/vmchecker/ui/?locale=en}{\textbf{Vmchecker}}.\vspace{1.5mm}\\
	Languages used: Prolog, Python, bash \vspace{1.0mm}\\
	\small{Reference to \textbf{Andrei Ismail} (PhD student, AI-MAS Group) - e-mail: \href{mailto:iandrei@gmail.com}{iandrei@gmail.com}}

    \vspace{1.2mm}\textbf{ROSEdu member} \hfill \textbf{August 2011 - present} \vspace{1.5mm}\\
	\href{http://rosedu.org/}{\textbf{ROSEdu}} (Romanian Open Source Education) is a community of 
	students from my university, passionate about IT and open-source. We develop 
	open-source projects and organize different events.\vspace{1mm}
	\begin{list2}
        \item Past coordinator of \textit{Open Source Development Course}, June 2011 - June 2012.
	\end{list2}\vspace{-3mm}
	\small{Reference to \textbf{Razvan Deaconescu} (ROSEdu Founder)
		- e-mail: \href{mailto:razvan.deaconescu@cs.pub.ro}{razvan.deaconescu@cs.pub.ro}}

	% \vspace{1.2mm}\href{https://github.com/andreip}{\textbf{github profile}}, coding for fun\hfill \textbf{April 2011 -- present}\vspace{1.5mm}\\
	% \vspace{1mm} \textsl{huffman compression, K-D tree, AI-MAS code, flask app.}

	% \vspace{1.2mm}\href{http://www.freedroid.org/}{\textbf{freedroid.org}} \hfill \textbf{March 2011}\vspace{1.5mm}\\
	% \vspace{1mm} \textit{My first committed open-source contribution during first college year, for GSoC.}\\
	% \small{Reference to \textbf{patch} for \textbf{freedroid.org} on -
	% 	\href{http://rb.freedroid.org/r/1024/}{reviewboard}}

%	LPIC
	\href{http://www.lpi.org/eng/certification/the\_lpic\_program/lpic\_1}{\textbf{Linux Professional Institute Certificate-1}}
		\hfill \textbf{February 2011 -- May 2011}\vspace{1.5mm}\\
	\vspace{1mm}\textit{Completed course by passing an internal exam.}\\
	\small{Reference to \textbf{Razvan Deaconescu} (PhD student, Computer Programming)
		- e-mail: \href{mailto:razvan.deaconescu@cs.pub.ro}{razvan.deaconescu@cs.pub.ro}}


    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming languages} 
    \textit{Good knowledge:} C\\
	\textit{Medium knowledge:} Python\\
	\textit{Beginner:} Prolog, bash, JavaScript, ruby, java, C++, Coffeescript

    %__________________________________________________________________________________________________________________
    % Other Activities

    \section{\mysidestyle Other\\Activities}

	\vspace{1.2mm}\href{http://www.scoutpanaitescu.ro/}{\textbf{Scouts member}}, Bucharest, Romania\vspace{1mm}\\
	Scouting seeks the formation of responsible young people available to contribute to building a better world, and we try 
	to do just that, by making use of entertaining activities like: hiking, camping, games, fire songs/stories, survival 
	techniques etc.\vspace{1.5mm}\\
	\textbf{\textit{Hobbies:}} swimming, hiking, chess, table tennis, reading

    % Referees
%    \section{\mysidestyle Referees} 
%    {\sl Available on request.}


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

