%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Andrei-Niculae Petre
\documentclass[line, margin]{resume}
\usepackage{nicefrac}

\RequirePackage{color}
%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% all this for a "~"
% https://tex.stackexchange.com/questions/9363/how-does-one-insert-a-backslash-or-a-tilde-into-latex#answer-9372
\newcommand{\bettertilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}


%______________________________________________________________________________________________________________________
\begin{document}

\renewcommand{\namefont}{ \LARGE \bf }

\name{Andrei-Niculae PETRE}

\address{\href{mailto:andrei@linux.com}{andrei@linux.com}}
\address{\href{http://andreipetre.ro}{andreipetre.ro}}

\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
%    \section{\mysidestyle Contact\\Information}

%    phone: +40 727 029 961              \\
%   phone: +358 41 362 6333              \\
%   phone: +1 650 353 13 74              \\
%    e-mail:  \href{mailto:p31andrei@gmail.com}{p31andrei@gmail.com} \vspace{0mm}\\\vspace{-4.5mm}\\%
%    website: \href{http://andreipetre.ro}{andreipetre.ro}, github: \href{https://github.com/andreip/}{andreip}, skype: andreip31

%__________________________________________________________________________________________________________________
    % About
    \section{About}

I'm excited about low-level programming and backend-oriented opportunities. I've got 4.5 years Java experience in AWS, 5 years Python experience as a full stack developer, 1.5 years C++ experience as a TA in university and an interest in open source, c(pp), python, golang, linux, rock climbing and chess. Check \href{http://andreipetre.ro}{my website} for a list of open source contributions. I'm also a member of \href{http://rosedu.org}{ROSEdu}, an organization that promotes open-source in education.

    %__________________________________________________________________________________________________________________
    % Professional Experience
\section{Experience}

\textbf{Senior SDE}, \href{https://www.keysight.com/}{Keysight}, Bucharest, Romania\hfill Aug 2023 - present\\
Having fun within OS/VM space with C programming and dpdk.

% SDE1 - Jan 2019 - March 2021
% SDE2 - April 2021 - May 2023
% ( SDE3 - tracking Jan 2024 )
\textbf{SDE}, \href{https://aws.amazon.com/}{AWS RDS}, Bucharest, Romania (Remote)\hfill Feb 2022 - May 2023\\
\textbf{SDE}, \href{https://aws.amazon.com/}{AWS RDS}, Vancouver, BC\hfill Jan 2019 - Feb 2022 \\
\href{https://aws.amazon.com/rds/}{Amazon Relational Database Service} (RDS) makes it easy to set up, operate, and scale a relational database in the cloud. It provides cost-efficient and resizable capacity while automating time-consuming administration tasks such as hardware provisioning, database setup, patching and backups.
\begin{itemize} \itemsep -2pt  % reduce space between items
    \item Designed and delivered \href{https://docs.aws.amazon.com/AmazonRDS/latest/UserGuide/USER_ReplicateBackups.html}{XRAB (Cross-Region Automated Backups)} - got a "Nice!" from Andy Jassy. Helped all RDS engine teams onboard XRAB, held L\&Ls / training sessions to other RDS teams and mentored a summer intern on the project.
    \item Led a team of 3 other engineers (and got excellent feedback from them on it) to build an internal CRUD service to achieve complex search queries and requirements needed for an AWS goal release. It relied on DynamoDB and Lambda with Go.
    \item Worked on security threat modelling for two projects: above CRUD service and \href{https://docs.aws.amazon.com/AmazonRDS/latest/UserGuide/oracle-efs-integration.html}{RDS EFS Integration for Oracle} project.
    \item I was one of the few (1\%) component owners of our RDS backend service. % 10 / 1000
\end{itemize}


\textbf{Software Engineer}, \href{https://www.ycombinator.com/companies/upbeat}{UpbeatPR}, Bucharest, Romania (Remote)\hfill Dec 2015 - March 2018\\
\textbf{Software Engineer Intern}, \href{https://www.ycombinator.com/companies/upbeat}{UpbeatPR}, San Francisco, CA\hfill Feb 2015 - Aug 2015\\
Highly targeted pitching process, enabled through our amounts of data we collected about\\ journalists -- PR without relationships.
\begin{itemize} \itemsep -2pt  % reduce space between items
    \item I was one of the first engineers at Upbeat, designed and built systems core to our business in Python, Django, Scrapy, Celery, ElasticSearch, Javascript (ES6), React, Redux and Ruby on Rails.
    \item Worked on all parts of delivering software: design, implementation, testing, deployment, continuous integration, maintenance, instrumentation and monitoring.
    \item Designed and implemented the data ingestion automation that powered our business. It started with a cost-effective feed poller (\bettertilde650K new urls per day from 20K scraped feeds), a site scraper and an indexing system relying on ElasticSearch (\bettertilde16M indexed articles) to provide our in-house PR agents a powerful tool for matching journalists with their area of expertise.
\end{itemize}

\textbf{Software Engineer}, \href{http://devlabel.com/}{dev.Label}\hfill Aug 2014 - Jan 2015\\
Worked on \href{https://www.trade.it/}{trade.it}, a multi-broker trading application (Groovy, JS, CoffeeScript, ChromeDriver).

% For my reference:
% OOP 		- Oct 2016 - Feb 2017
% SD  		- Mar 2016 - Jun 2017 (x2)
% PP & SD	- Mar 2014 - Jun 2014
% AA		- Oct 2013 - Feb 2014
\textbf{Teaching Assistant}, POLITEHNICA University of Bucharest\hfill 2013 -- 2014, 2016 -- 2017\\
Taught Data Structures \& Algorithms class for 3 years, using C++. Also taught 3 other classes: Object Oriented Programming, Functional Programming and Complexity Analysis of Algorithms.

\textbf{Software Engineer}, \href{http://ubervu.com}{UberVU} (acquired by HootSuite, \bettertilde15M\$) \hfill Jun 2012 -- Aug 2013\\
Social media analytics, monitoring and engaging dashboard.
\begin{itemize} \itemsep -2pt  % reduce space between items
%	\item Started working at uberVU while still in college, and picked up best practices and new technologies I've never worked with before with tremendous speed.
	\item Started as a Frontend Engineer, working on our in-house \href{https://github.com/uberVU/mozaic/}{mozaic.JS} (backbone.js based) framework that enabled the new interface that would lead to the acquisition of uberVU, just 4 months after my leave
    \item Then also working on the REST API for the JS frontend, using Django, Tastypie and mySQL
    \item Lastly, worked on the Python backend pipeline that collected and indexed data into MongoDB and ElasticSearch, as well as on our CI system and deployment scripts
\end{itemize}

%    \vspace{1.2mm}\textbf{Artificial Intelligence \& Multi-Agent Systems Lab Intern}
%        \hfill Jun 2011 -- Sept 2011\vspace{1mm}\\
%    {\fontsize{2.65mm}{1em}\selectfont
%      Developed a homework for the Politehnica University AI class in Prolog while a first-year student.
%    }


%__________________________________________________________________________________________________________________
    % Education
    \section{Education}

    %\textbf{MSc}, Machine Learning and Data Mining\hfill Sept 2014 - paused\\
    %\textbf{Aalto University}, Finland\\
    %School of Science

    \textbf{BSc}, Major in Engineering and Computer Science\hfill Oct 2010 - July 2014\\
    \textbf{University POLITEHNICA of Bucharest}, Romania\\
    Faculty of Automatic Control and Computer Science
    %__________________________________________________________________________________________________________________
    % Computer Skills
    %\section{\mysidestyle Computer\\Skills}

% \section{Skills}
%
% \begin{tabular}[t]{@{} p{1.7in} p{3.8in} @{}}
% \bf{In Production:} & Python, Django, Flask, ElasticSearch, mongo, Scrapy, Celery\\
%     				& JS, nodeJS, React, Redux, CoffeeScript, jQuery, Backbone.js\\
%                     & Git, Bash shell scripting, Heroku, PostgreSQL, ChromeDriver\\
%                     & Groovy, Grails, Ruby on Rails\\
% \bf{TA \& personal projects:} & C, C++, Java\\
% % \bf{In open source course:} & C \& GObject for Anjuta, a Gnome IDE, during an open source course, \href{http://cdl.rosedu.org/}{CDL}\\
% \bf{For fun:} & Go, Scheme, Haskell, Prolog\\
% \bf{Certifications:} & Linux (LPIC-1)
% \end{tabular}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
